Offline Mode for Corporate Mobile Client Security Architecture

### 2017-09-30 docs/papers/2016MONE-Final/2016MONE.tex
adding all

\begin{acknowledgements}
The authors thank the Brazilian research and innovation agencies CAPES (Grant FORTE \\23038.007604/2014-69), FAPDF (Research Support Foundation of the Federal District), FINEP (Grant RENASIC PROTO 01.12.0555.00), CNPq (Productivity grant 303905/2014-0 and PVE Grant 88881.030392/2013-01), as well as the European CSF - Aerospace Technology Program (PDE scholarship within project 207644/2015-2), for their support to this research.\end{acknowledgements}

>>>>

\begin{acknowledgements}
This research work has the support of the Brazilian research and innovation Agencies CAPES - Coordination for the Improvement of Higher Education Personnel (Grant 23038.007604/2014-69 FORTE - Tempestive Forensics Project), FINEP - Funding  Authority for Studies and Projects (Grant 01.12.0555.00 RENASIC/PROTO - Secure Protocols Laboratory of the National Information Security and Cryptography Network) and FAPDF - Research Support Foundation of the Federal District (Grants 0193.001366/\\2016 UIoT - Universal Internet of Things and 0193.001365/\\2016 - Secure Software Defined Data Center - SSDDC), as well as the Ministry of Planning, Development and Management (Grants 005/2016 DIPLA - Planning and Management Directorate, and 11/2016 SEST - Secretariat of State-owned Federal Companies) and the DPGU - Brazilian Union Public Defender (Grant 066/2016).
\end{acknowledgements}
